Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya

### 2022-06-13 Detailed_analyses_for_paper.Rmd
corresponds to the first draft of methods

for (i in 1:nrow(x_balance_intervention))
{
  if (rbinom(1, 1, balance_adoption_rate)) # if farmers adopt, make changes in x file
    {x_balance_intervention$milk_yield_5[i]<-x_balance_intervention$milk_yield_5[i]+0.75
     x_balance_intervention$milk_yield_6[i]<-x_balance_intervention$milk_yield_6[i]+0.75
     x_balance_intervention$feed_prod_CO2[i]<-x_balance_intervention$feed_prod_CO2[i]-(328.5 * 
                    sum(x_Calliandra_intervention[i,paste0("N_animal_type_",1:12)]))
  }
}
# run model for modified x file
balance_res <- run_model(x_balance_intervention, ghg_emissions)

>>>>

for (i in 1:nrow(x_balance_intervention))
{
  if (rbinom(1, 1, balance_adoption_rate)) # if farmers adopt, make changes in x file
    {x_balance_intervention$milk_yield_5[i]<-x_balance_intervention$milk_yield_5[i]+0.75
     x_balance_intervention$milk_yield_6[i]<-x_balance_intervention$milk_yield_6[i]+0.75
     x_balance_intervention$feed_prod_CO2[i]<-x_balance_intervention$feed_prod_CO2[i]-(328.5 * 
                    sum(x_balance_intervention[i,paste0("N_animal_type_",1:12)]))
  }
}
# run model for modified x file
balance_res <- run_model(x_balance_intervention, ghg_emissions)
